Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-26 awipev-CO2.Rmd
Added ESSD figure pCO2

```{r ESSD time series, echo=FALSE, message= FALSE, warning=FALSE}
mytheme <- function(size_labs = 6, face_font="plain", ...) {
  theme_bw() +
  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
        axis.title.x = element_text(face=face_font, size=size_labs, margin=margin(0,0,0,0,"pt")),
        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
        axis.title.y = element_text(face=face_font, size=size_labs),
        axis.ticks.x = element_line(size=0.1),
        axis.ticks.y = element_line(size=0.1),
        axis.ticks.length = unit(1.1, "mm"),
        panel.grid.major = element_line(size = 0.25, color="black", linetype="dotted"),
        aspect.ratio = 1 / 3,
        plot.margin = margin(t = 0, r = 1, b = 0, l = 0, unit = "lines")
  )
}

xlim <- c(as.POSIXct("2015-07-01 00:00:00"), as.POSIXct("2020-07-01 00:00:00"))
# calculate omeaga arag
z <- d_all %>% 
  dplyr::filter(!(is.na(pco2_corr) | is.na(at_calc) | is.na(sal_mix) |is.na(temp_insitu_11m) | is.na(pressure_insitu_ctd)))
oa_tbf <- as_tibble(
  carb(24, z$pco2_corr, z$at_calc*1e-6, S = z$sal_mix, T = z$temp_insitu_11m, 
                          P = z$pressure_insitu_ctd/10, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", 
                          ks = "d", pHscale = "T", b = "u74")
) %>% 
  dplyr::mutate(datetime = z$datetime,
                oa = OmegaAragonite) %>% 
dplyr::select(datetime, oa)
# select time series data and add Omega
d <- as_tibble(d_all) %>%
  dplyr::select(datetime, pressure_insitu_ctd, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, 
                ph_dur_corr, at_calc)
d <- left_join(d, oa_tbf, by = 'datetime')

@@

# ts_sal / ts_temp / ts_at
# grid.arrange(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ncol = 1)
# cowplot::save_plot(filename = "figures/ts_sp.pdf", plot = cp)
# multiplot(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, cols = 1)
```
```{r ESSD boxplots, echo=FALSE, message= FALSE, warning=FALSE}
mytheme_bp <- function(size_labs = 9, face_font="plain", ...) {
  mytheme() +
    theme_bw() +
  theme(aspect.ratio = 1/2,
        plot.margin = margin(t = -2, r = 0.2, b = -2, l = 0, unit = "cm"),
        axis.text.x=element_blank())
  }
d_long <- d %>% 
  dplyr::mutate(month = as.factor(month(x = datetime, label = TRUE))) %>% 
  tidyr::pivot_longer(-c(datetime, month), names_to = "variable", values_to = "value")

sal_mix_bp <- ggplot(filter(d_long, variable=="sal_mix"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = "Salinity") +
  mytheme_bp()
temp_11m_bp <- ggplot(filter(d_long, variable=="temp_insitu_11m"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = "Temp. 11 m (°C)") +
  mytheme_bp()
pco2_bp <- ggplot(filter(d_long, variable=="pco2_corr"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
  mytheme_bp()
ph_bp <- ggplot(filter(d_long, variable=="pHint_tot_sf"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste("p", H[T]))) +
  mytheme_bp()
at_bp <- ggplot(filter(d_long, variable=="at_calc"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
  mytheme_bp() +
  theme(axis.text.x = element_text(vjust = 1))
oa_bp <- ggplot(filter(d_long, variable=="oa"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste(Omega[a]))) +
  mytheme_bp() +
  theme(axis.text.x = element_text(vjust = 1))
g <- cowplot::plot_grid(sal_mix_bp, temp_11m_bp, pco2_bp, ph_bp, at_bp, oa_bp, ncol=2,
               align="v")
ggsave(file="figures/boxplots.png", g,  width = 18, height = 14, units = "cm")
```

>>>>

```{r ESSD time series, echo=FALSE, message= FALSE, warning=FALSE}
mytheme <- function(size_labs = 6, face_font="plain", ...) {
  theme_bw() +
  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
        axis.title.x = element_text(face=face_font, size=size_labs, margin = margin(0,0,0,0,"pt")),
        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
        axis.title.y = element_text(face=face_font, size=size_labs),
        axis.ticks.x = element_line(size=0.1),
        axis.ticks.y = element_line(size=0.1),
        axis.ticks.length = unit(1.1, "mm"),
        panel.grid.major = element_line(size = 0.25, color="grey50", linetype="dashed"),
        panel.grid.minor = element_line(size = rel(0.5), color = "grey50", linetype="dotted"),
        aspect.ratio = 1 / 3,
        plot.margin = margin(t = 0, r = 1, b = 0, l = 0, unit = "lines")
  )
}

xlim <- c(as.POSIXct("2015-07-01 00:00:00"), as.POSIXct("2020-07-01 00:00:00"))
# calculate omeaga arag
z <- d_all %>% 
  dplyr::filter(!(is.na(pco2_corr) | is.na(at_calc) | is.na(sal_mix) |is.na(temp_insitu_11m) | is.na(pressure_insitu_ctd)))
oa_tbf <- as_tibble(
  carb(24, z$pco2_corr, z$at_calc*1e-6, S = z$sal_mix, T = z$temp_insitu_11m, 
                          P = z$pressure_insitu_ctd/10, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", 
                          ks = "d", pHscale = "T", b = "u74")
) %>% 
  dplyr::mutate(datetime = z$datetime,
                oa = OmegaAragonite) %>% 
dplyr::select(datetime, oa)
# select time series data and add Omega
d <- as_tibble(d_all) %>%
  dplyr::select(datetime, pressure_insitu_ctd, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, 
                ph_dur_corr, pco2_calc_insitu, at_calc)
d <- left_join(d, oa_tbf, by = 'datetime')

@@

# ts_sal / ts_temp / ts_at
# grid.arrange(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ncol = 1)
# cowplot::save_plot(filename = "figures/ts_sp.pdf", plot = cp)
# multiplot(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, cols = 1)
```
```{r ESSD boxplots, echo=FALSE, message= FALSE, warning=FALSE}
mytheme_bp <- function(size_labs = 9, face_font="plain", ...) {
  mytheme() +
  theme(aspect.ratio = 1/2,
        plot.margin = margin(t = -2, r = 0.2, b = -2, l = 0, unit = "cm"),
        axis.text.x=element_blank())
  }
d_long <- d %>% 
  dplyr::mutate(month = as.factor(month(x = datetime, label = TRUE))) %>% 
  tidyr::pivot_longer(-c(datetime, month), names_to = "variable", values_to = "value")

sal_mix_bp <- ggplot(filter(d_long, variable=="sal_mix"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = "Salinity") +
  mytheme_bp()
temp_11m_bp <- ggplot(filter(d_long, variable=="temp_insitu_11m"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = "Temp. 11 m (°C)") +
  mytheme_bp()
pco2_bp <- ggplot(filter(d_long, variable=="pco2_corr"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
  mytheme_bp()
ph_bp <- ggplot(filter(d_long, variable=="pHint_tot_sf"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste("p", H[T]))) +
  mytheme_bp()
at_bp <- ggplot(filter(d_long, variable=="at_calc"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
  mytheme_bp() +
  theme(axis.text.x = element_text(vjust = 1))
oa_bp <- ggplot(filter(d_long, variable=="oa"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y = expression(paste(Omega[a]))) +
  mytheme_bp() +
  theme(axis.text.x = element_text(vjust = 1))
g <- cowplot::plot_grid(sal_mix_bp, temp_11m_bp, pco2_bp, ph_bp, at_bp, oa_bp, ncol=2,
               align="v")
ggsave(file="figures/boxplots.png", g,  width = 18, height = 14, units = "cm")
```
```{r ESSD pCO2, echo=FALSE, warning=FALSE, message=FALSE}
fit <- lmodel2(data = d,  pco2_corr ~ pco2_calc_insitu , nperm = 99)

p <-  ggplot(d, aes(x=pco2_calc_insitu, y= pco2_corr)) +
  geom_point(color = "blue") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]), colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  coord_fixed(ratio = 1 ,xlim=c(200, 400) , ylim=c(200, 400))+
  labs(x = expression(paste("Calculated pC", O[2], " (", mu, "atm)")), y = expression(paste("In situ pC", O[2], " (", mu, "atm)"))) + 
  mytheme(size_labs = 10) +
    theme(aspect.ratio=1, plot.title = element_text(size=7))
ggsave(file="figures/pco2.png", p,  width = 14, height = 14, units = "cm")
```
